Adaptive broadcast tree for multicores

### 2013-06-28 paper.tex
Moving to Laptop

% configuration
\usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes,fit,backgrounds}
\pgfplotsset{width=.9\linewidth}
\usepgfplotslibrary{external}
%\tikzexternalize

@@

\fancyhf{}
\fancyfoot[L]{\today}
\pagestyle{fancy}

@@

>>>>

% configuration
\usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes,fit,backgrounds}
\pgfplotsset{width=.9\linewidth}
\usepgfplotslibrary{external}
\tikzexternalize

@@

\fancyhf{}
\fancyfoot[L]{\today}
\fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\pagestyle{fancy}

@@

\subsection{Pairwise performance}

Figure~\ref{pgfplot:20130627} shows the UMP RTT time for each pair of
cores. The benchmark seems to be broken, since sending messages to
core 40 and higher is really expensive. On the other hand. Sending
messages from these cores back to cores with low IDs (which are on the
other end of the machine) seems unreasonably cheap.

What we would expect is a symmetric plot. Sending a message from core
$n$ to $m$ should be about equally expensive than sending a message
from $m$ to $n$.

\pgfplotsset{width=\linewidth}
\begin{figure}
  \caption{pair-wise latency for appenzeller}
  \label{pgfplot:20130627}
  \begin{tikzpicture}
    \begin{axis}[
      zlabel={cost [cycles]},
      xlabel={sending core},
      ylabel={receiving core},
      scaled z ticks = false,
      z tick label style={/pgf/number format/fixed}
      ]
    \addplot3[surf] file {measurements/appenzeller_pairwise_ump.dat};
    \end{axis}
  \end{tikzpicture}
\end{figure}

\pgfplotsset{width=\linewidth}
\begin{figure}
  \caption{pair-wise latency for gottardo}
  \label{pgfplot:20130627}
  \begin{tikzpicture}[scale=.75]
    \begin{axis}[scaled z ticks=false,z tick label style={/pgf/number format/fixed},zlabel={cost [cycles]},xlabel={sending core},ylabel={receiving core}]
    \addplot3[surf] file {measurements/gottardo_pairwise_ump.dat};
    \end{axis}
  \end{tikzpicture}
\end{figure}
